

```{bash}
# Experimented with another way to load the data - not intuitive, just keeping for the file accession numbers
# prefetch <SRR19782039> #Valsartan exposed
# prefetch <SRR13013756> #hypoxia
# prefetch <SRR7725722> #DSP toxins
# prefetch <SRR16771870> #17 a-Ethinylestradiol (EE2)
```


```{bash}
#keeping this chunk here to remind me where my BLAST is located, DO NOT RUN
# cd /home/shared/8TB_HDD_02/cnmntgna/Applications/bioinfo/
# curl -O https://ftp.ncbi.nlm.nih.gov/blast/executables/blast+/LATEST/ncbi-blast-2.13.0+-x64-linux.tar.gz
# tar -xf ncbi-blast-2.13.0+-x64-linux.tar.gz
```

```{bash}
#Project path
 ls /home/shared/8TB_HDD_02/cnmntgna/GitHub/chris-musselcon

```

```{bash}

```

```{bash}

#keeping to redo database if necessary
# cd /home/shared/8TB_HDD_02/cnmntgna/data
# curl -O https://ftp.uniprot.org/pub/databases/uniprot/current_release/knowledgebase/complete/uniprot_sprot.fasta.gz
# mv uniprot_sprot.fasta.gz uniprot_sprot_r2023_01.fasta.gz
# gunzip -k uniprot_sprot_r2023_01.fasta.gz
# ls /home/shared/8TB_HDD_02/cnmntgna/data
```

```{bash}
# keeping for database purposes
#/home/shared/8TB_HDD_02/cnmntgna/Applications/bioinfo/ncbi-blast-2.13.0+/bin/makeblastdb \
#-in /home/shared/8TB_HDD_02/cnmntgna/data/uniprot_sprot_r2023_01.fasta \
#-dbtype prot \
#-out /home/shared/8TB_HDD_02/cnmntgna/output/blastdb/uniprot_sprot_r2023_01
```

Query Sequence 1: Exposure to Valsartan & Carbamazepine
```{bash}
#Query sequence 1: 
curl https://trace.ncbi.nlm.nih.gov/Traces/?run=SRR19782039 \
-k \
> /home/shared/8TB_HDD_02/cnmntgna/GitHub/chris-musselcon/data/VC-Exposure
```

Query Sequence 2: Exposure to a synthetic hormone 17 a-Ethinylestradiol (EE2)
```{bash}
# I know I need to put the sequences in a folder, but there has to be a format mistake I am making to get this in here.
#Query sequence 1: 
curl https://trace.ncbi.nlm.nih.gov/Traces/?run=SRR19782039 \
-k \
> /home/shared/8TB_HDD_02/cnmntgna/Github/chris-musselcon/data/EE2
```

Query Sequence 3: Diarrhetic Shellfish Poisoning (DSP) toxins associated with Harmful Algal Blooms (HABs)
```{bash}
#Query sequence 1: 
curl https://trace.ncbi.nlm.nih.gov/Traces/?run=SRR19782039 \
-k \
> home/shared/8TB_HDD_02/cnmntgna/Github/chris-musselcon/data/DSP-HAB
```

Query Sequence 4: Hypoxia
```{bash}
#Query sequence 1: 
curl https://trace.ncbi.nlm.nih.gov/Traces/?run=SRR19782039 \
-k \
> home/shared/8TB_HDD_02/cnmntgna/Github/chris-musselcon/data/Hypoxia
```
I  HAVE NOT ALTERED ANY OF THE CODE BELOW TO REFLECT MY PROJECT SEQUENCES
```{bash}
head ../home/shared/8TB_HDD_02/cnmntgna/data/Ab_4denovo_CLC6_a.fa
echo "How many sequences are there?"
grep -c ">" ../data/Ab_4denovo_CLC6_a.fa
```

```{bash}
/home/shared/8TB_HDD_02/cnmntgna/Applications/bioinfo/ncbi-blast-2.13.0+/bin/blastx \
-query ../data/Ab_4denovo_CLC6_a.fa \
-db ../blastdb/uniprot_sprot_r2023_01 \
-out ../output/Ab_4-uniprot_blastx.tab \
-evalue 1E-20 \
-num_threads 20 \
-max_target_seqs 1 \
-outfmt 6
```

```{bash}
head -2 ../home/shared/8TB_HDD_02/cnmntgna/output/Ab_4-uniprot_blastx.tab
wc -l /home/shared/8TB_HDD_02/cnmntgna/output/Ab_4-uniprot_blastx.tab
```

```{bash}
curl -O "Accept: text/plain; format=tsv" "https://rest.uniprot.org/uniprotkb/search?query=reviewed:true+AND+organism_id:9606"
```

```{bash}
curl -O -H "Accept: text/plain; format=tsv" "https://rest.uniprot.org/uniprotkb/stream?compressed=true&fields=accession%2Creviewed%2Cid%2Cprotein_name%2Cgene_names%2Corganism_name%2Clength%2Cgo_f%2Cgo%2Cgo_p%2Cgo_c%2Cgo_id%2Ccc_interaction%2Cec%2Cxref_reactome%2Cxref_unipathway%2Cxref_interpro&format=tsv&query=%28%2A%29%20AND%20%28reviewed%3Atrue%29"
```

```{bash}
head -2 /home/shared/8TB_HDD_02/cnmntgna/output/Ab_4-uniprot_blastx.tab
wc -l ../output/Ab_4-uniprot_blastx.tab
```

```{bash}
tr '|' '\t' < /home/shared/8TB_HDD_02/cnmntgna/output/Ab_4-uniprot_blastx.tab | head -2
```

```{bash}
tr '|' '\t' < /home/shared/8TB_HDD_02/cnmntgna/output/Ab_4-uniprot_blastx.tab \
> ../output/Ab_4-uniprot_blastx_sep.tab
```

```{bash}
head -2 /home/shared/8TB_HDD_02/cnmntgna/data/uniprot_table_r2023_01.tab
wc -l ../data/uniprot_table_r2023_01.tab
```

```{r}
library(tidyverse)
install.packages("kableExtra")
library("kableExtra")
```

```{r}
bltabl <- read.csv("../output/Ab_4-uniprot_blastx_sep.tab", sep = '\t', header = FALSE)
spgo <- read.csv("../data/uniprot_table_r2023_01.tab", sep = '\t', header = TRUE)
str(spgo)
```

```{r}
kbl(
head(
  left_join(bltabl, spgo,  by = c("V3" = "Entry")) %>%
  select(V1, V3, V13, Protein.names, Organism, Gene.Ontology..biological.process., Gene.Ontology.IDs) %>% mutate(V1 = str_replace_all(V1, 
            pattern = "solid0078_20110412_FRAG_BC_WHITE_WHITE_F3_QV_SE_trimmed", replacement = "Ab"))
)
) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

```{r}
left_join(bltabl, spgo,  by = c("V3" = "Entry")) %>%
  select(V1, V3, V13, Protein.names, Organism, Gene.Ontology..biological.process., Gene.Ontology.IDs) %>% mutate(V1 = str_replace_all(V1, 
            pattern = "solid0078_20110412_FRAG_BC_WHITE_WHITE_F3_QV_SE_trimmed", replacement = "Ab")) %>%
  write_delim("../output/blast_annot_go.tab", delim = '\t')
```

```{r}
annot_tab <- read.csv("../output/blast_annot_go.tab", sep = '\t', header = TRUE)
```



Start here for the 'try it myself' code

```{r}

library(DESeq2)
library(Rsubread)

# Set the working directory to where the FASTQ files are located
setwd("<path/to/FASTQ/files>")

# Load the FASTQ files
files <- list.files(pattern=".fastq.gz$")
names(files) <- gsub(".fastq.gz$", "", files)
samples <- data.frame(sampleName = names(files), fileName = files)

# Align the reads to a reference genome
index <- "path/to/reference/genome"
align <- align(index, files, output.format="BAM", nthreads=8)

# Perform differential gene expression analysis
countTable <- featureCounts(files, annot.ext="path/to/gene/annotation", isGTFAnnotationFile=TRUE, nthreads=8)
dds <- DESeqDataSetFromMatrix(countData=countTable[, 7:ncol(countTable)], colData=samples, design=~sampleName)
dds <- DESeq(dds)
res <- results(dds)
```
=======
Section 1 - load library
Section 2 - pull data files
Section 3 - replicate 4/4 workflow for qc

>>>>>>> 9f6ea84556eae9e3ac73969033039c7bc337ed77

