---
title: "Blasting CDS for Gene Annotation"
author: Chris
date: "`r format(Sys.time(), '%d %B, %Y')`"  
output: 
  html_document:
    theme: readable
    highlight: zenburn
    toc: true
    toc_float: true
    number_sections: true
    code_folding: show
    code_download: true
editor: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
library(knitr)
library(tidyverse)
library(kableExtra)
library(DESeq2)
library(pheatmap)
library(RColorBrewer)
library(data.table)
library(DT)
library(Biostrings)
knitr::opts_chunk$set(
  echo = TRUE,         # Display code chunks
  eval = FALSE,         # Evaluate code chunks
  warning = FALSE,     # Hide warnings
  message = FALSE,     # Hide messages
  fig.width = 6,       # Set plot width in inches
  fig.height = 4,      # Set plot height in inches
  fig.align = "center" # Align plots to the center
)
```

```{r}
getwd()
```
```{r, engine='bash', eval=TRUE}

 cd /home/shared/8TB_HDD_02/cnmntgna/GitHub/chris-musselcon/data/ncbi_dataset/data/GCA_900618805.1
 head cds_from_genomic.fna
 
```

#going to call my existing uniprot database made in week 2 to blast my cds file
#fix my paths for reproducibility purposes

```{r, engine='bash'}


/home/shared/8TB_HDD_02/cnmntgna/Applications/bioinfo/ncbi-blast-2.13.0+/bin/blastx \
-query /home/shared/8TB_HDD_02/cnmntgna/GitHub/chris-musselcon/data/ncbi_dataset/data/GCA_900618805.1/cds_from_genomic.fna \
-db /home/shared/8TB_HDD_02/cnmntgna/output/blastdb/uniprot_sprot_r2023_01 \
-out /home/shared/8TB_HDD_02/cnmntgna/data/cds_blastx.tab \
-evalue 1E-20 \
-num_threads 20 \
-max_target_seqs 1 \
-outfmt 6
```
```{bash}

head /home/shared/8TB_HDD_02/cnmntgna/data/cds_blastx.tab

```


# The results from my blast will come out like the line below. Some of the categories that may be represented are listed below the sample line
Sample line
lcl|UYJE01000001.1_cds_VDH88702.1_13    sp|Q8BSY0|ASPH_MOUSE    46.124  258     137     2       1633   2406     316     571     3.38e-57        212

Some categoreis of assessment
Query ID: The identifier of the sequence submitted as the query for the BLAST search.
Subject ID: The UniProtKB accession number of the hit sequence that the query matched.
% Identity: The percentage of identical amino acids or nucleotides between the query and hit sequence.
Alignment length: The length of the alignment between the query and hit sequence.
E-value: The expected value, which is a measure of the statistical significance of the match.
Bit score: A measure of the similarity between the query and hit sequences.
Query coverage: The percentage of the query sequence that is covered by the alignment.
Subject description: The description of the hit sequence.
Taxonomy ID: The NCBI taxonomy identifier of the organism to which the hit sequence belongs.
Gene name: The name of the gene that encodes the hit sequence.

url="https://gannet.fish.washington.edu/seashell/snaps/uniprot_table_r2023_01.tab"  

file_path=" /home/shared/8TB_HDD_02/cnmntgna/GitHub/chris-musselcon/data"    # Replace with your desired file path
```{bash}

wget -O "uniprot_table_r2023_01.tab" "https://gannet.fish.washington.edu/seashell/snaps/uniprot_table_r2023_01.tab"

```

```{bash}

mv /home/shared/8TB_HDD_02/cnmntgna/GitHub/chris-musselcon/code/uniprot_table_r2023_01.tab  /home/shared/8TB_HDD_02/cnmntgna/GitHub/chris-musselcon/data

mv /home/shared/8TB_HDD_02/cnmntgna/GitHub/chris-musselcon/output/DEGlist.tab
/home/shared/8TB_HDD_02/cnmntgna/GitHub/chris-musselcon/data

```


```{r}
#needed this to make the cds table accessible
cdsBlastx <- read.delim("/home/shared/8TB_HDD_02/cnmntgna/GitHub/chris-musselcon/data/cds_blastx.tab", sep = "\t", header= FALSE)


# Write the data to a comma-separated values (CSV) file
#cds<- write.csv(cdsBlastx, "cds.csv", row.names= FALSE)
#view(cds)


```


```{bash}

head -2 ../code/cds.csv
wc -l ../code/cds.csv

```

```{bash}
tr '|' '\t' < ../code/cds.csv | head -2
```

```{bash}
tr '|' '\t' < ../code/cds.csv \
> ../data/cds.csv
```

```{bash}

head ../data/cds.csv
```

```{bash}
head -2 ../output/DEGlist.tab
wc -l ../output/DEGlist.tab
```
```{bash}
tr '|' '\t' < ../output/DEGlist.tab | head -2
```

```{bash}
tr '|' '\t' < ../output/DEGlist.tab \
> ../data/DEGlist.tab
```

```{bash}

head ../data/DEGlist.tab

```
```{bash}

head ../data/cds.tab

```
trying to merge cds and DEGlist before merging with uniprot table
```{r}
# Assuming you have a data frame named "df"
num_columns <- ncol("cds.tab")
print(num_columns)

```
trying to merge cds and DEGlist before merging with uniprot table
```{r}
# Assuming you have a data frame named "df"
num_rows <- nrow("cds.tab")
print(num_rows)

```


going to verify everything is formatted correctly since no column nor row is showing up
```{r}
getwd()
cds <- read.table("/home/shared/8TB_HDD_02/cnmntgna/GitHub/chris-musselcon/data/cds.tab", sep = "\t", header = FALSE)
deg <- read.table("/home/shared/8TB_HDD_02/cnmntgna/GitHub/chris-musselcon/data/DEGlist.tab", sep = "\t", header = TRUE)


```
extract the actual term i need from cds before i merge with deg.
```{r}
library(tidyverse)

# Read the TSV file into a data frame
cds1 <- read.table("/home/shared/8TB_HDD_02/cnmntgna/GitHub/chris-musselcon/data/cds.tab", sep = "\t", header = FALSE)

# Separate the column into multiple columns based on a delimiter
cds2 <- separate(cds1, V2, into = c("Column 1", "Column 2", "Column 3"), sep = "\t")

# Write the updated data frame back to a TSV file
write.table(cds2, file = "/home/shared/8TB_HDD_02/cnmntgna/GitHub/chris-musselcon/data/newcds.tab", sep = "\t", row.names = FALSE)
```

trying to fix deg column data being used as row names
```{r}
# Create a new column with the values from row names
deg$column_name <- rownames(deg)

# Reset the row names to default numeric indices
rownames(deg) <- NULL
```


```{r}

cdsDEG <- merge(cds2, deg, by.x = 1, by.y = 7 )
head(cdsDEG)
```
prep uniprot table for joining
```{bash}
head -2 ../data/uniprot_table_r2023_01.tab
wc -l ../data/uniprot_table_r2023_01.tab
```

prep uniprot table for joining
```{r}
uni<- read.csv("../data/uniprot_table_r2023_01.tab", sep = '\t', header = TRUE)
  
```
/home/shared/8TB_HDD_02/cnmntgna/GitHub/chris-musselcon/data/uniprot_table_r2023_01.tab

```{r}
library(kableExtra)
library(knitr)
library(dplyr)
library(readr)

# Generate table
kbl(
  head(
    left_join(cdsDEG, uni , by = c("Column 2" = "Entry")) %>%
      select(V3, V4, pvalue, Protein.names, Organism, Gene.Ontology..biological.process., Gene.Ontology.IDs))
) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

#table_content<- capture.output(table)

#table_content <- gsub("^\\s+", "", table_content)

# Save table as tab-delimited file
#write_lines(table_content, "/home/shared/8TB_HDD_02/cnmntgna/GitHub/chris-musselcon/data/table.tab")

```

```{bash}

head ../data/table.tab

```

